A game theoretic model of the behavioural gaming that takes place at the EMS - ED interface

### 2021-09-24 sections/model_overview/main.tex
Make changes suggested by proselint
Apply changes based on Alex's suggestions
Minor changes to other sections

The third player, the distributor has their own choices to make and their own 
goals to satisfy.
The strategy set of the third player is the proportion \(0 \leq p \leq 1\) of 
individuals it sends to the first queueing system (the proportion \(1 - q\) is 
sent to the second queueing system).
In addition, the distributor aims to minimise any potential blockages
that may occur, given the pair of thresholds chosen by the two queueing systems.
Thus, its objective is to minimise the blocked time of the individuals 
that they send to the two queueing systems.
Apart from the time being blocked, an additional aspect that may affect the 
decision of the distributor is the proportion of lost individuals.
Equation \ref{eq:obj-distributor} can be used to capture a mixture 
between the two objectives.

\begin{equation}\label{eq:obj-distributor}
    \alpha P(L_A) + (1 - \alpha) B_A = 
    \alpha P(L_B) + (1 - \alpha) B_B
\end{equation}

@@

Using equations \ref{eq:obj-queueing-systems} and \ref{eq:obj-distributor} gives
an imperfect information extensive form game. 
An imperfect information game is defined as an extensive form game where some 
of the information about the game state is hidden for at least one of the 
players~\cite{Berwanger2008}. In this study the state of the problem that is
hidden is the threshold that each of the first two players chooses to play.
In other words, each queueing system chooses to play a strategy without the 
knowing the other system's strategy.
The distributor then, fully aware of the chosen threshold strategies, distributes 
individuals among the two systems in order to minimise the time that its 
individuals will be blocked. Figure \ref{fig:imperfect-info-game} illustrates this.

\begin{figure}[ht]
    \centering
    \begin{tikzpicture}[-, node distance = 3cm, scale=0.8]
        \node[anchor=north](HA){\(H_A\)};
        \node[anchor=north](HA_d1) at (3, 2){.};
        \node[anchor=north](HA_d2) at (3, -2){.};

@@

        \node[anchor=north](HB) at (4.1, 0){\(H_B\)};
        \node[anchor=north](HB_d1) at (6.9, 2){.};
        \node[anchor=north](HB_d2) at (6.9, -2){.};

@@

The first 
queueing system \(H_A\) decides on a threshold, then the second system \(H_B\)
chooses its own threshold, without knowing the strategy of \(H_A\), and finally
the distributor makes its choice. Note here that the dotted line represents the
fact that \(H_B\) is unaware of the state of the game when making its own 
decisions. The game can thus be partitioned into a normal form game between the
two queueing systems and finding the distributor's best choice.

@@

\begin{equation}
    U_{T_1, T_2}^i = \quad -\left( 
        \hat{P} - P(W_i < R) 
    \right)^2
\end{equation}

@@

\begin{equation} \label{eq:payoff-matrices}
    A = 
    \begin{pmatrix}
        U_{1,1}^A & U_{1,2}^A & \dots & U_{1,N_B}^A \\
        U_{2,1}^A & U_{2,2}^A & \dots & U_{2,N_B}^A \\
        \vdots & \vdots & \ddots & \vdots \\
        U_{N_A,1}^A & U_{N_A,2}^A & \dots & U_{N_A,N_B}^A \\
    \end{pmatrix},
    B = 
    \begin{pmatrix}
        U_{1,1}^B & U_{1,2}^B & \dots & U_{1,N_B}^B \\
        U_{2,1}^B & U_{2,2}^B & \dots & U_{2,N_B}^B \\
        \vdots & \vdots & \ddots & \vdots \\
        U_{N_A,1}^B & U_{N_A,2}^B & \dots & U_{N_A,N_B}^B \\
    \end{pmatrix}
\end{equation}

>>>>

The third player, the distributor has their own choices to make and their own 
goals to satisfy.
The strategy set of the third player is the proportion \(0 \leq p \leq 1\) of 
individuals it sends to the first queueing system (the proportion \(1 - q\) is 
sent to the second queueing system).
In addition, the distributor aims to minimise any potential blockages
that may occur, given the pair of thresholds chosen by the two queueing systems.
Thus, its objective is to minimise the blocked time of the individuals 
that they send to the two queueing systems.
Apart from the time being blocked, an additional aspect that may affect the 
decision of the distributor is the proportion of lost individuals.
Equation \ref{eq:obj_distributor} can be used to capture a mixture 
between the two objectives.

\begin{equation}\label{eq:obj_distributor}
    \alpha P(L_A) + (1 - \alpha) B_A = 
    \alpha P(L_B) + (1 - \alpha) B_B
\end{equation}

@@

Using equations \ref{eq:obj-queueing-systems} and \ref{eq:obj_distributor} gives
an imperfect information extensive form game. 
An imperfect information game is defined as an extensive form game where some 
of the information about the game state is hidden for at least one of the 
players~\cite{Berwanger2008}. In this study the state of the problem that is
hidden is the threshold that each of the first two players chooses to play.
In other words, each queueing system chooses to play a strategy without the 
knowing the other system's strategy.
The distributor then, fully aware of the chosen threshold strategies, distributes 
individuals among the two systems in order to minimise the time that its 
individuals will be blocked. Figure \ref{fig:imperfect-info-game} illustrates this.

\begin{figure}[ht]
    \centering
    \begin{tikzpicture}[-, node distance = 3cm, scale=0.8]
        \node[anchor=north](HA){\(Q_A\)};
        \node[anchor=north](HA_d1) at (3, 2){.};
        \node[anchor=north](HA_d2) at (3, -2){.};

@@

        \node[anchor=north](HB) at (4.1, 0){\(Q_B\)};
        \node[anchor=north](HB_d1) at (6.9, 2){.};
        \node[anchor=north](HB_d2) at (6.9, -2){.};

@@

The first 
queueing system \(Q_A\) decides on a threshold, then the second system \(Q_B\)
chooses its own threshold, without knowing the strategy of \(Q_A\), and finally
the distributor makes its choice. Note here that the dotted line represents the
fact that \(Q_B\) is unaware of the state of the game when making its own 
decisions.

@@

\begin{equation} \label{eq:payoff-entry}
    U_{T_1, T_2}^i = \quad -\left( 
        \hat{P} - P(W_i < R) 
    \right)^2
\end{equation}

@@

\begin{equation} \label{eq:payoff_matrices}
    A = 
    \begin{pmatrix}
        U_{1,1}^A & U_{1,2}^A & \dots & U_{1,N_B}^A \\
        U_{2,1}^A & U_{2,2}^A & \dots & U_{2,N_B}^A \\
        \vdots & \vdots & \ddots & \vdots \\
        U_{N_A,1}^A & U_{N_A,2}^A & \dots & U_{N_A,N_B}^A \\
    \end{pmatrix},
    B = 
    \begin{pmatrix}
        U_{1,1}^B & U_{1,2}^B & \dots & U_{1,N_B}^B \\
        U_{2,1}^B & U_{2,2}^B & \dots & U_{2,N_B}^B \\
        \vdots & \vdots & \ddots & \vdots \\
        U_{N_A,1}^B & U_{N_A,2}^B & \dots & U_{N_A,N_B}^B \\
    \end{pmatrix}
\end{equation}
